\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-06-22 manuscript/main.tex
update teh result

Lianjia, the largest real estate brokerage in China, has revolutionized real estate transactions through the establishment of the Beke platform. This platform enables rapid expansion by integrating offline stores on a large scale while leveraging the advantages of resource sharing. However, prior to 2018, the platform Beke primarily focused on facilitating listings from Lianjia's offline stores and aimed to attract buyers from the market. However, in 2018, Beke established a new strategy named Agent Cooperate Network (ACN), which integrates and shares the content across its multiple subsidiaries to realize multiple revenue models simultaneously.\footnote{The ACN model disaggregates the transaction process into specialized tasks handled by individual agents or stores. These tasks include seller-side activities such as sourcing sellers, maintaining property listings, commission negotiations, and buyer-side activities like client acquisition, property-client matching, transaction facilitation, and financial services assistance.}

Through the ACN model, Lianjia transforms internal competition within the system into overall system competitiveness, thereby enhancing the brand's reputation and market influence. More importantly, this strategic allows Lianjia to cooperate with other previously competitors by consolidating resources and forms a consolidation. For instance, data from AutoNavi Map and CREIS indicate that in 2020, although only about 20\% of real estate agent stores in the main urban area of Chengdu City are Lianjia's offline stores, these stores achieved a market share of 73.98\%. This remarkable market penetration underscores the efficacy of Beke's integrated platform and ACN model in dominating the real estate brokerage landscape. The Table \ref{tab:precise_proportion_contraction} shows the comparision of the market share of Lianjia and the share of the number of stores in the market.

@@

While sellers may consider a multi-homing strategy—listing their property with multiple brokerages—this approach is suboptimal for several reasons. Firstly, the exclusivity of contracts between sellers and agents often precludes the adoption of a multi-homing strategy. Secondly, although sellers can list their properties with multiple brokerages, smaller agencies frequently lack a sufficiently broad client base, limiting their effectiveness in selling homes.Thirdly, engaging multiple brokers simultaneously can lead to reduced incentives among agents, as they perceive competition for the same property, diminishing their proactive efforts. Finally, while service cost variations between agencies are acknowledged, these costs are minor compared to the property's value and are more closely related to the risks associated with holding a financial asset. Consequently, risk-averse sellers are inclined to choose an agency that provides a guaranteed level of service.

@@

To assess the consolidation effect of the online platform, we treat the year Lianjia implemented the Agent Cooperate Network (ACN) strategy as an exogenous shock to the market. Our findings reveal that this strategy substantially boosts revenues and alters consumer behaviors, particularly in the number of house tours facilitated by the brokerage. These results underscore the necessity for a synergistic evolution of online and offline strategies in the real estate brokerage market. Furthermore, they indicate that the online consolidation effect is becoming increasingly significant relative to the offline clustering effect.

>>>>

Lianjia, the largest real estate brokerage in China, has revolutionized real estate transactions through the establishment of the Beke platform. This platform enables rapid expansion by integrating offline stores on a large scale while leveraging the advantages of resource sharing. However, prior to 2018, the platform Beke primarily focused on facilitating listings from Lianjia's offline stores and aimed to attract buyers from the market. However, in 2014, Beke established a new strategy named Agent Cooperate Network (ACN), which integrates and shares the content across its multiple subsidiaries to realize multiple revenue models simultaneously.\footnote{The ACN model disaggregates the transaction process into specialized tasks handled by individual agents or stores. These tasks include seller-side activities such as sourcing sellers, maintaining property listings, commission negotiations, and buyer-side activities like client acquisition, property-client matching, transaction facilitation, and financial services assistance.} Moreover, in 2018, Lianjia decided to enhance its Agent Cooperation Network (ACN) strategy by incorporating smaller brokerages into its network and launching franchise stores under the brand name Deyou, along with other smaller formats. This strategic move aimed to increase network effects and further consolidate the platform, thereby enhancing market power and operational efficiency.

Through the success of the platform consolidation, Lianjia transforms internal competition within the system into overall system competitiveness, thereby enhancing the brand's reputation and market influence. More importantly, this strategic allows Lianjia to cooperate with other previously competitors by consolidating resources. For instance, data from AutoNavi Map and CREIS indicate that in 2020, although only about 20\% of real estate agent stores in the main urban area of Chengdu City are Lianjia's offline stores, these stores achieved a market share of 73.98\%. This remarkable market penetration underscores the efficacy of Beke's integrated platform and ACN model in dominating the real estate brokerage landscape. The Table \ref{tab:precise_proportion_contraction} shows the comparision of the market share of Lianjia and the share of the number of stores in the market.

@@

While sellers might consider a co-listing strategy—listing their property with multiple brokerages—this approach is suboptimal for several reasons within China's real estate market. Despite previous literature, such as \citep{RePEc:kap:jrefec:v:67:y:2023:i:3:d:10.1007_s11146-021-09858-w}, indicating that the co-listing can be beneficial for clients under multiple-listing service. Specifically in China's real estate market, firstly, the exclusivity of contracts between sellers and agents often precludes the adoption of a co-listing strategy. Secondly, although sellers can list their properties with multiple brokerages, smaller agencies frequently lack a sufficiently broad client base, limiting their effectiveness in selling homes. Thirdly, engaging multiple brokers simultaneously can lead to reduced incentives among agents, as they perceive competition for the same property, diminishing their proactive efforts. Finally, while service cost variations between agencies are acknowledged, these costs are minor compared to the property's value and are more closely related to the risks associated with holding a financial asset. Consequently, risk-averse sellers are inclined to choose an agency that provides a guaranteed level of service.

@@

To assess the consolidation effect of the online platform, we treat the year Lianjia implemented the platform consolidation strategy as an exogenous shock to the market. The platform consolidation strategy is majorly based on the Agent Cooperation Network (ACN) framework of Lianjia, where Lianjia can divide the process of transaction to multiple agents. Our findings reveal that this strategy substantially boosts revenues and alters consumer behaviors, particularly in the number of house tours facilitated by the brokerage. These results underscore the necessity for a synergistic evolution of online and offline strategies in the real estate brokerage market. Furthermore, they indicate that the online consolidation effect is becoming increasingly significant relative to the offline clustering effect.
